---
title: "Buoy Observations of Air And Sea Temperatures in The Southern Bering Sea"
author: "Tiffany Cheng, Xiru Lyu"
date: "3/9/2018"
output: ioslides_presentation
---
```{r setup, include=FALSE,warning=FALSE}
knitr::opts_chunk$set(echo = FALSE)
source('Part 1.R')
```

## Air Temperature

```{r,warning=FALSE,fig.width=8.5}
plot.ATMP
```


## Air Temperature (Cont.) {.larger}

## Sea Temperature

```{r, warning=FALSE,fig.width=8.5}
plot.WTMP
```

## Sea Temperature (Cont.) {.larger}


## Relationship Between Air Temperature and Sea Temperature

```{r,warning=FALSE,fig.width=8.5}
plot.mixed
```

## Relationship Between Air and Sea Temperatures (Cont.)

- The previous plot shows that air and sea temperatures are highly correlated, as they two follow a very similar pattern over time. In addition, the sea temperature is always above 0ºC and is generally higher than the air temperature each day. 

- A further check for the correlation between two variables with the following code yields the result of `r corr`, which confirms our findings from the plot.

      ```
      cor(tidy$ATMP, tidy$WTMP, use = 'complete.obs')
      ```

## Issue with Missing Data

