---
title: "Buoy Observations of Air And Sea Temperatures in The Southern Bering Sea"
author: "Tiffany Cheng, Xiru Lyu"
date: "3/9/2018"
output: ioslides_presentation
---
```{r setup, include=FALSE,warning=FALSE}
knitr::opts_chunk$set(echo = FALSE)
source('Part 1.R')
```


## Background

## Air Temperature

```{r,warning=FALSE,fig.width=8.5}
plot.ATMP
```

- There is a seasonal pattern repeating every year, and the air temperature is generally between -10ºC and 10ºC.

## Has the mean air temperature changed for past 30 years? {.smaller}

- We used the mean air temperature every year to conduct a one-way ANOVA test to see if it changes over time.

  $$H_{0}: \mu_{1985} = \mu_{1986} = \mu_{1987} = ... = \mu_{2017}$$
  $$H_{a}: At\ least\ one\ \mu_i\ is\ different$$
```{r}
oneway.test(ATMP ~ Year, data = tidy)
```

- With a significance level of 0.05, the result of the test suggests that there is a statistically significant change in mean air temperature in the past 30 years.

## Sea Temperature

```{r, warning=FALSE,fig.width=8.5}
plot.WTMP
```

- There is a seasonal pattern repeating every year, and the sea temperature is generally always above 0ºC.

## Has the mean sea temperature changed for past 30 years? {.smaller}

- We used the mean sea temperature every year to conduct a one-way ANOVA test to see if it changes over time. 

  $$H_{0}: \mu_{1985} = \mu_{1986} = \mu_{1987} = ... = \mu_{2017}$$
  $$H_{a}: At\ least\ one\ \mu_i\ is\ different$$
  
```{r}
oneway.test(WTMP ~ Year, data = tidy)
```

- With a significance level of 0.05, the result of the test suggests that there is a statistically significant change in mean sea temperature in the past 30 years.

## Relationship Between Air Temperature and Sea Temperature

```{r,warning=FALSE,fig.width=8.5}
plot.mixed
```

## Relationship Between Air and Sea Temperatures (Cont.)

- The previous plot shows that air and sea temperatures are highly correlated, as they both follow a very similar pattern over time. In addition, the sea temperature is always above 0ºC and is generally higher than the air temperature each day. 

- A further check for the correlation between two variables with the following code yields the result of `r corr`, which is very high and confirms our findings from the plot.

      ```
      cor(tidy$ATMP, tidy$WTMP, use = 'complete.obs')
      ```

## Issue with Missing Data



## Conclusion
